dplyr---
title: "Mini Project 3"
author: "Emily Kim, Dasom An, Janell Lin"
date: "4/8/2018"
output: html_document
---

```{r}

library(tidyverse)
library(macleish)

#Install macleish
#devtools::install_github("beanumber/macleish")

# Install macleish
devtools::install_github("beanumber/macleish")



library(tidyverse)
library(macleish)
library (dplyr)

library(sf)

library(sf)
library(lwgeom)
```

```{r}


trails <- macleish_layers[["trails"]] %>%
  mutate(computed_length = st_length(geometry))

macleish_layers[["trails"]]

head(trails)

plot(macleish_layers[["trails"]])

trails_1<- trails %>%
  group_by(name) %>%
  summarize(num_segments = n(), 
            total_length = sum(computed_length)) %>%
  arrange(desc(total_length))

name <- c('Snowmobile Trail','Eastern Loop','Easy Out', "entry trail","Poplar Hill Road","Porcupine Trail", "Vernal Pool Loop","Western Loop")
numeric_rating <- c(47.73311, 24.99817, 2.4, 4.0, 21.49414,16.71984,5.4, 27.56704)

difficulty_rating <- data.frame(name, numeric_rating, stringsAsFactors=FALSE)%>%
  mutate (Difficulty= if_else(as.numeric(numeric_rating)<10, "Easy", ifelse(as.numeric(numeric_rating)<30, "Moderate", "Hard")))

trails_2 <-trails_1  %>%
  inner_join(difficulty_rating, by = "name")

contours <- macleish_layers[["contours_3m"]] 
```


```{r}


#elevation
elevation <- st_read("CONTOURS250K_ARC.shp")


library(macleish)
packageVersion("macleish")
library(sp)

names(macleish_layers)

library(sf)
elevation <- st_read("CONTOURS250K_ARC.shp")

contours <- macleish_layers[["contours_3m"]] %>%
  dplyr::select(ELEV_M, ELEV_FT, INDEX_ARC, SHAPE_LEN, geometry)

elevation_trail_xings <- macleish_layers[["trails"]] %>%
  st_intersection(macleish_layers[["contours_3m"]]) %>%
  dplyr::select(ELEV_M, ELEV_FT, INDEX_ARC, SHAPE_LEN, geometry, name, color) %>%
  dplyr::group_by(name) %>%
  dplyr::summarise(max = max(ELEV_FT), min = min(ELEV_FT), n = n()) %>%
  dplyr::mutate(difference = max - min)%>%
  dplyr::mutate (Difficulty= if_else(difference<100, "Easy", ifelse(difference<200, "Moderate", "Hard")))
  

landmarks<- macleish_layers[["landmarks"]]


library (leaflet)

pal <- colorNumeric(
  palette = "blue",
  domain = contours$ELEV_M)

factpal <- colorFactor(topo.colors(3), palette = c('red', 'orange', 'green'),trails_2$Difficulty)

require(leaflet)

leaflet()%>%
  addTiles()%>%
  addPolylines(data=trails_2, 
               weight = 5, fillOpacity = 0.5,
               popup = ~ name, group = "Structures",
               color = ~factpal(Difficulty))%>%
  addMarkers(data = macleish_layers[["landmarks"]], 
             popup = ~ Label, group = "Structures")%>%
  addPolylines(data = contours, weight = 1, fillOpacity = 0.1, color = ~pal(ELEV_M))









```


Questions:
1. Cannot plot contours
2. How to visualize difficulty on the map with two variables
3. How to remove units


4.  including relevant external information in your analysis
5. develop a heuristic that will classify these (or any other) trails based on their difficulty.

```{r}
#the_crs <- crs(trails, asText = TRUE)

#st_crs(elevation)
#st_crs(trails)

st_crs(elevation)
st_crs(trails)

#library(sf)



library(raster)

the_crs <- crs(trails, asText = TRUE)
elevation_crs <- st_transform(trails, crs = the_crs)

#View(contours)
```

%>%
  mutate (Difficulty= if_else(as.numeric(total_length)<1000, "Easy", ifelse(as.numeric(total_length)<2000, "Moderate", "Hard")))












=======
unzip(local_file, exdir = "contours250k")
```
=======
>>>>>>> 1bb2015a5e6b02c15658c91f5ffd291063fc8dc4

```{r fig.show="hold", fig.width=3}
#put all the figures together
```

>>>>>>> ca8071ab7d9b03cb0d8859eb10adfe7e84ab723b
